---
title: "Case study for Bayesian Statistics"
author: |
    | 姓名1(学号)
    | 姓名2(学号)
#date: "`r format(Sys.time(), '%B %d, %Y')`"
documentclass: ctexart
fontsize: 12pt
geometry: tmargin=1.8cm, bmargin=1.8cm, lmargin=2.1cm, rmargin=2.1cm
output:
#  pdf_document:  
  rticles::ctex:
    keep_tex: true
    fig_caption: yes
    number_sections: yes
    toc: yes
    latex_engine: xelatex
classoption: "hyperref,"
header-includes: 
#  - \usepackage{fontspec, xunicode, xltxtra}    
  - \usepackage{ctex}
  - \usepackage{bm,xcolor}
  - \usepackage{fancyhdr}
  
  - \pagestyle{fancy}
  - \fancyhead[L]{Case study for Bayesian Statistics}
  - \fancyfoot[R]{\thepage}
  - \fancyfoot[C]{School of Statistics, ECNU}  
# 设置页眉线与页脚线宽度与颜色
  - \renewcommand{\headrule}{{\color{red}\hrule width\headwidth height\headrulewidth \vskip-\headrulewidth}}
  - \renewcommand{\footrule}{{\color{black}\vskip-\footruleskip\vskip-\footrulewidth \hrule width\headwidth height\footrulewidth\vskip\footruleskip}}
  - \renewcommand{\headrulewidth}{0.8pt}
  - \renewcommand{\footrulewidth}{0.6pt}
  - \renewcommand\contentsname{\bfseries Contents}  
# 定制章节标题格式 
  - \usepackage[sf,raggedright]{titlesec}
  - \usepackage{titletoc}
  - \titleformat{\section}{\bfseries\large\color{blue}}{\bfseries\thesection}{0.5em}{}
#  - \titleformat{\subsection}{\bfseries\large}{\bfseries\thesubsection}{0.5em}{}
  - \titlespacing{\section}{0pt}{3.5ex plus .1ex minus .2ex}{1.5\wordsep}
#  - \titlespacing{\subsection}{0pt}{1.5ex plus .1ex minus .2ex}{\wordsep}
# hyperline
  - \hypersetup{colorlinks=true, breaklinks=true, linkcolor=blue}
---

\newpage
\addcontentsline{toc}{section}{Abstract}
\noindent\textbf{Abstract}:
State the background of the study, data, methodology and main conclusions.

**Keywords**: 3-5 keywords 

\newpage

# Data description

State the data source, data structure, response variable, predictive variables, etc. 



# Methods used in data analysis

## Maximum likelihood estimation

## EM algorithm

## Bayesian inference based on MCMC



#  Data exploration and statistical analysis

## Data exploration

## Statistical analysis

## Comparison of the different methods


# Main results

## Simulation study

## Real data analysis


1. Suppose the uniform distribution $Beta(2, 5)$ is used for the success probability $p$ of Kobe Bryant, what is posterior distribution of $p$? Plot the prior, likelihood and posterior density on the same graph in R. 

```{r}
kobe <- read.csv("/Users/yctang/Rdata/kobe.csv", header = TRUE)

s = sum(kobe$basket == "H")
f = sum(kobe$basket == "M")
a = 2; b = 5
# R code for question 1.
curve(dbeta(x,a,b),
      xlim=c(0, 1), ylim=c(0,10), 
      xlab="p",ylab="Density",
      lty=3,lwd=2) #prior
curve(dbeta(x,s+1,f+1),
      add=TRUE,lty=2,lwd=2) #likelihood
curve(dbeta(x,a+s,b+f),  
      add=TRUE, lty=1,lwd=2) # posterior 
legend(.7,4,c("Prior","Likelihood","Posterior"),
lty=c(3,2,1),lwd=c(3,3,3))
```

1. Suppose Kobe Bryant would play a new game the following quarter and he made 20 shots. Draw a sample of size 1000 from the posterior predictive distribution of $p$, and plot the frequencies. Compare (on the graph)  with the analytic result based on the posterior predictive distribution. 


```{r}
# R code for question 2.
m = 1000
ns = 20
p = rbeta(m, a+s, b+f)
y = rbinom(m, ns, p)
#y = rbb(m, ns, a+s, b+f)
freq = table(y)
ys = as.integer(names(freq))
predprob = freq/sum(freq)
plot(ys, predprob, type="h", xlab="y",
ylab="Predictive Probability")
library(LearnBayes)
TruePred1 = pbetap(c(a+s,b+f), ns, ys)
points(ys, TruePred1, type="p", col='red')
```

1. Calculate the 95\% equal-tail and HPD (highest posterior density) posterior credible intervals of $p$ based on the posterior sample.  Compare with the analytic results based on the posterior density. Fill the results in the table below.

```{r, message=FALSE}
# R code for question 3.
round(quantile(p,  prob= c(0.025, 0.975)),4)
round(qbeta(c(0.025, 0.975), a+s, b+f ),4)
library(TeachingDemos)
round(emp.hpd(p, conf=0.95),4)
round(hpd(qbeta, shape1 = a+s, shape2 = b+f, conf = 0.95),4)
```

# Conclusions and remarks

Main conclusions comes here!

\addcontentsline{toc}{section}{References}
\noindent\textbf{References}

1. 吴喜之. 统计学: 从数据到结论(第四版). 中国统计出版社. 2013. 

1. Larry Wasserman. All of Statistics--A Concise Course in Statistical Inference. 2003. (中译本---张波等. 统计学完全教程. 科学出版社. 2008.) [github上有习题的R/python代码]

1. David S. Moore， Willian I. Notz， Michael A. Fligner. The Basic Practive of Statistics (6th Ed.). W.H. Freeman and Company. 2013. 

